### 2016-05-13 paper/paper.tex
add torpath ref, (need text) and finish conclusion

@@

The relatively-short history of cryptocurrency is an exciting one, litered with
mystery

>>>>

TorPath~\cite{torpath} ... \TK

@@

Cryptocurrency inovation continues to produce new and useful proof-of-work
replacements. Still, proving access to arbitrary resources remains a difficult
challenge. In this direction, DDoSCoin delivers a novel technique for proving
the use of bandwidth to a (potentially unwilling) target domain. We hope that
this work encourages others to discover and inovate on novel proof-of-resource
puzzles.
